ChIP-seq datasets for FDR benchmarking

### 2017-12-20 datasets/ChIP-seq/ChIP-seq.Rmd
ChIP-seq

### Testing differential ChIP-seq signals between two cell lines (K562 *vs.* Gm12878)
These two cell lines hold the largest sequencing datasets on ENCODE project. 
We chose histone H3K4Me3 ChIP-seq data for our analysis here.

@@

We download the bam files directly from UCSC ENCODE protal.

@@

@@

@@

@@

Now, we're ready to construct the `SummarizedBenchmark` object, which will run
the functions specified in each method (these are actually sourced in from the
                                        helper scripts).

>>>>

### Testing differential ChIP-seq signals between two cell lines (K562 *vs.* Gm12878)

These two cell lines hold the largest sequencing datasets in ENCODE project. 
We chose histone H3K4Me3 ChIP-seq data for our analysis here.

@@

We downloaded the bam files directly from UCSC ENCODE protal.

@@

Here, we first load in all R-packages needed in the analysis. As 
mentioned above, classical differential analysis pipeline would 
involve peak calling as the first step. In that case, differential 
testing is performed on a filtered set of genomic regions after 
peak calling. However, this will result in limited null tests since 
regions are chosen with significance at least in one condition. 
To address this issue, we selected ChIP-seq data of H3K4Me3 which is 
an active marker of gene expression. We focus our analysis on 
promoter regions of all genes for this histone marker. This helps 
avoid limited null tests with peak calling by not losing
most interesting regions for this histone marker.

@@

Basically, we count sequencing reads for all promoter regions here.
We chose the average coverage across conditions and replicates as the covariate.

@@

Here, we can see that the covariant variable is actually informative.
As we know, ChIP-seq data always involves two sets of regions: 
signal and background. Sometimes, there are a few regions with 
signal coverage between signal and background. In this example, 
we see that p-values are differently distributed under low, 
median and high coverage.

@@

Now, we're ready to construct the `SummarizedBenchmark` object, which will run
the functions specified in each method.
